Opportunities for improvement in adult trauma patients admitted to the intensive care unit: A registry-based study

### 2024-01-11 manuscript.Rmd
11/1

@@

Variables and data sources/measurements
---------------------------------------
Study outcome
-------------
The study outcome will be on the presence of OFI in adult patients treated in the ICU focusing on different types of opportunities for improvement including delayed treatment, judgement error and technical errors...

Patient and process factors 
---------------------------
The factors were chosen from the trauma registry, based on the locally used audit filters, standard epidemiological factors and factors registered in the Swedish National Trauma Registry. The categorical factors were sex, survival after 30 days, Glasgow Coma Scale (GCS), respiratory rate, systolic blood pressure, working hours, weekend, time from arrival at the hospital until first computed tomography (CT) and if the patient was intubated. The continuous factors age and Injury Severity Score (ISS) were also included. Working hours was defined as between 8.00 a.m. and 5 p.m., or during a weekend, defined as Saturday or Sunday.

@@

Study size 
----------
<!-- Explain how the study size was arrived at -->

Quantitative variables
----------------------
<!-- Explain how quantitative variables were handled in the
analyses. If applicable, describe which groupings were chosen and why
-->

>>>>

Setting
-------
The Karolinska University Hospital in Solna is a level 1 trauma centre based on the definition by the American College of Surgeons (ACS) Committee on Trauma [5], and is designated to receive all patients in Stockholm with major or suspected major trauma. The hospital has direct access to radiology, surgery, emergency medicine, intensive care and consultants from relevant specialities [6]. All patients are included in a mortality and morbidity screening combining individual review and specific audit filters by specialized nurses. The patients who are identified as having higher probability for OFI are discussed in a multidisciplinary conference held every 6-8 weeks. Examples of OFI include the need for better organization or more senior members taking part in the trauma care. The presence or absence of OFI is decided among the participants of the conference and then recorded in the trauma care quality database.

@@

Variables and data sources/measurements
---------------------------------------

### Study outcome
The study outcome will be on the presence of OFI in adult patients treated in the ICU focusing on different types of opportunities for improvement including delayed treatment, judgement error and technical errors...

### Patient and process factors 
The factors were chosen from the trauma registry, based on the locally used audit filters, standard epidemiological factors and factors registered in the Swedish National Trauma Registry. The categorical factors were sex, survival after 30 days, Glasgow Coma Scale (GCS), respiratory rate, systolic blood pressure, working hours, weekend, time from arrival at the hospital until first computed tomography (CT) and if the patient was intubated. The continuous factors age and Injury Severity Score (ISS) were also included. Working hours was defined as between 8.00 a.m. and 5 p.m., or during a weekend, defined as Saturday or Sunday.

@@

Study size 
----------

<!-- Read up on the sample size requirements of logistic regression. You will come across for example the 10 events per variable rule, which is sometimes used as a rule of thumb to decide the size of the model in comparison to available data. You can also read up on the concept of power. -->

<!-- Explain how the study size was arrived at -->

Quantitative variables
----------------------
*senare*

<!-- Age, ISS, time from arrival to CT, systolic blood pressure, respiratory rate and GCS score can all be considered quantitative variables. Describe how they were handled in the analyses. -->

<!-- Explain how quantitative variables were handled in the
analyses. If applicable, describe which groupings were chosen and why
-->
